---
title       : Global Biodiversity 
subtitle    : Mapping the geographic distribution of species using the GBIF API
author      : C. Ribeiro
job         : Data Analyst
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
logo        : GBIF_logo_short_form.gif
knit        : slidify::knit2slides
---

## Global Biodiversity Information Facility (GBIF)

### GBIF's vision

**"A world in which biodiversity information is freely and universally available for science, society and a sustainable future."**

+ International open data infrastructure, funded by governments.

+ It provides a single point of access to more than 400 million records related to evidence of more than one million species.

+ Biggest biodiversity database on the Internet.

+ `rgbif` is an R package to search and retrieve biodiversity data using the public GBIF API.

---

## Example

### Ursus americanus

The American black bear (Ursus americanus) is a medium-sized bear native to North America. It is the continent's smallest and most widely distributed bear species.

`name_backbone()` is used to search against the GBIF backbone taxonomy:

```{r echo=TRUE, tidy_source=TRUE}
suppressPackageStartupMessages(library(rgbif))

sp <- name_backbone(name='Ursus americanus', rank='species')
# Classification
cat(paste(sp[c("kingdom","phylum","class","order","family","genus","species")]),sep=",")

```

---

## Example

### Ursus americanus

You can also search for subspecies using `name_suggest()`
```{r echo=TRUE, tidy_source=TRUE}
name_suggest(q='Ursus americanus',limit=6)
```

---

## Slide 5

Get taxonomic key
key <- name_backbone(name='Puma concolor')$speciesKey
dat <- occ_search(taxonKey=key, return='data', limit=300)




